The Tail Risk Premium - Extension of Lottery Preference Premium

### 2025-03-25 416 Tables Complete.qmd
Add files via upload

@@

slide14_table <- slide14_data %>% 
  summarise(
    across(c(Base, New, NewSubBase), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(Base, New, use = "complete.obs")
  )

@@

summary_table_14 %>% 
   gt() %>% 
  fmt_percent(
    columns = where(is.numeric), # Apply only to numeric columns
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), # Filter only Mean, StDev, and Max
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 # Adjust to desired decimal places
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 # Adjust to desired decimal places
  )

@@

slide17_table <- slide17_data %>% 
  summarise(
    across(c(BaseLong, NewLong, NewSubBaseLong), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(BaseLong, NewLong, use = "complete.obs")
  )

@@

summary_table_17 %>% 
  gt() %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

@@

slide18_table <- slide18_data %>% 
  summarise(
    across(c(BaseShort, NewShort, NewSubBaseShort), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(BaseShort, NewShort, use = "complete.obs")
  )

@@

summary_table_18 %>% 
  gt() %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

@@

slide21_summary_table %>%
  gt() %>%
  fmt_number(
    columns = where(is.numeric), 
    decimals = 2 
  )
```

@@

slide21_summary_table_SKEW %>%
  gt() %>%
  fmt_number(
    columns = where(is.numeric), 
    decimals = 2 
  )
```

@@

```{}
```

@@

##
BenchIVOL_df <- read.csv("FINAL_NOT_SUCKY.csv", colClasses = c("date" = "character")) %>% 
  mutate(date = as.Date(zoo::as.yearmon(date, "%Y%m"), frac = 1),
         hi20 = hi20 / 100,
         lo20 = lo20 / 100,
         fammaPort = (hi20 + lo20) / 2
         ) %>% 
  dplyr::select(date, fammaPort)

@@

slide23_data <- slide23_data %>% 
  summarise(
    across(c(New, Base, fammaPort, SPY.RETURNS, rf.rate), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(Base, New, use = "complete.obs")
  )

summary_table_23 <- slide23_data %>%
  pivot_longer(everything(), names_to = c("Column", "Metric"), names_sep = "_", values_to = "Value") %>%
  pivot_wider(names_from = Column, values_from = Value)

summary_table_23 %>% 
   gt() %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

>>>>

![](images/clipboard-1227717430.png)

@@

slide14_table <- slide14_data %>% 
  summarise(
    across(c(Base, New, NewSubBase), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Min = ~ min(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(Base, New, use = "complete.obs")
  )

@@

summary_table_14 %>% 
   gt() %>% 
  cols_label(
    NewSubBase = "New - Base"
  ) %>%
  fmt_percent(
    columns = where(is.numeric), # Apply only to numeric columns
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), # Filter only Mean, StDev, and Max
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 # Adjust to desired decimal places
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 # Adjust to desired decimal places
  )

@@

slide17_table <- slide17_data %>% 
  summarise(
    across(c(BaseLong, NewLong, NewSubBaseLong), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Min = ~ min(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(BaseLong, NewLong, use = "complete.obs")
  )

@@

summary_table_17 %>% 
  gt() %>% 
  cols_label(
    BaseLong = "Base Long",
    NewLong = "New Long",
    NewSubBaseLong = "New Long -  Base Long"

  ) %>%
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

@@

slide18_table <- slide18_data %>% 
  summarise(
    across(c(BaseShort, NewShort, NewSubBaseShort), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Min = ~ min(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(BaseShort, NewShort, use = "complete.obs")
  )

@@

summary_table_18 %>% 
  gt() %>%
  cols_label(

    BaseShort = "Base Short",
    NewShort = "New Short",
    NewSubBaseShort = "New - Base"
  ) %>%

  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

@@

slide21_summary_table %>%
  gt() %>%cols_label(
    LongPosV1 = "Base IVOL Long",
    LongPosV2 = "New IVOL Long",
    ShortPosV1 = "Base IVOL Short",
    ShortPosV2 = "New IVOL Short"
  ) %>%
  fmt_number(
    columns = where(is.numeric), 
    decimals = 2 
  )
```

@@

slide21_summary_table_SKEW %>%
  gt() %>%
  cols_label(
    LongPosV1 = "Base Skew Long",
    LongPosV2 = "New Skew Long",
    ShortPosV1 = "Base Skew Short",
    ShortPosV2 = "New  Skew Short"
  ) %>%

  fmt_number(
    columns = where(is.numeric), 
    decimals = 2 
  )
```

@@

```         
```

@@

##
BenchIVOL_df <- read.csv("https://raw.githubusercontent.com/boykowealth/TailRiskPremium_PortfolioConcept/refs/heads/main/FINAL_NOT_SUCKY.csv", colClasses = c("date" = "character")) %>% 
  mutate(date = as.Date(zoo::as.yearmon(date, "%Y%m"), frac = 1),
         hi20 = hi20 / 100,
         lo20 = lo20 / 100,
         fammaPort = (hi20 + lo20) / 2
         ) %>% 
  dplyr::select(date, fammaPort)

@@

# Compute Summary Stats
slide23_summary <- slide23_data %>% 
  summarise(
    across(c(New, Base, fammaPort, SPY.RETURNS, rf.rate), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Min = ~ min(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    ))
  )

# Add Correlation rows manually
correlations <- slide23_data %>%
  summarise(
    Base = cor(New, Base, use = "complete.obs"),
    fammaPort = cor(New, fammaPort, use = "complete.obs"),
    SPY.RETURNS = cor(New, SPY.RETURNS, use = "complete.obs"),
    rf.rate = cor(New, rf.rate, use = "complete.obs"),
    New = 1  # Perfect correlation with self
  ) %>%
  pivot_longer(everything(), names_to = "Column", values_to = "Value") %>%
  mutate(Metric = "Correlation")

# Calculate difference stats vs. New
diff_stats <- slide23_data %>%
  summarise(
    across(c(Base, fammaPort, SPY.RETURNS, rf.rate), 
           list(
             DiffMean = ~ mean(New - .x, na.rm = TRUE),
             DiffTStat = ~ {
               diff <- New - .x
               mean(diff, na.rm = TRUE) / (sd(diff, na.rm = TRUE) / sqrt(sum(!is.na(diff))))
             }
           ), .names = "{.col}_{.fn}")
  ) %>%
  pivot_longer(everything(), 
               names_to = c("Column", "Metric"), 
               names_sep = "_", 
               values_to = "Value") %>%
  mutate(Metric = case_when(
    Metric == "DiffMean" ~ "Mean of Difference w.r.t. New",
    Metric == "DiffTStat" ~ "T-Stat of Difference w.r.t. New"
  )) %>%
  pivot_wider(names_from = Column, values_from = Value)

# Tidy + Pivot for GT table
summary_table_23 <- slide23_summary %>%
  pivot_longer(everything(), names_to = c("Column", "Metric"), names_sep = "_", values_to = "Value") %>%
  bind_rows(correlations) %>% 
  pivot_wider(names_from = Column, values_from = Value)
summary_table_23 <- bind_rows(summary_table_23, diff_stats)

summary_table_23 %>% 
  gt() %>% 
  cols_label(
    New = "New Strategy",
    Base = "Base Strategy",
    fammaPort = "Fama-French Benchmark",
    SPY.RETURNS = "S&P 500 Returns",
    rf.rate = "Risk-Free Rate"
  ) %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation", "Mean of Difference w.r.t. New"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat", "T-Stat of Difference w.r.t. New"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )
